### 2020-02-18 ChapterResults/chapterResults.tex
Updated: Removed [t] from result graph figures
Updated: Many changes to results

\section{Scalability Experiments}
This study aims to measure and demonstrate scalability of AP. When more servers are added, the timeliness of the simulation improves and more objects may be supported. The performance measure of interest is the maximum frame time of a server as this indicates if the simulation can be maintained when object numbers increase (keeping a low frame-time is the goal). Therefore, an injection rate is used, that spawns moving objects into the simulation as time passes.

@@

From these observations it may be declared that this system is scalable in column configuration as the addition of servers results in increased performance.

@@

\section{Collision Correctness Experiments}
In the following section we explore the correctness of collisions between objects, i.e. do objects have the same collision behaviour in a AP as they do in a centralised system. We are concerned with objects that are migrating and/or interacting with an object that has recently migrated.

Erroneous collisions fall into two categories:
\begin{itemize}
	\item Missed collisions, collisions that should have taken place but were not detected by the physics engine e.g. Bullet through paper problem.
	\item Late collisions, collisions that were detected later than they should have been and result in not only different collision results, but also unstable collision response.
\end{itemize}

@@

We will now explain how a naïve system can lead to erroneous collision behaviour and AP can lead to erroneous collision behaviour if speed, frame-time, or latency exceed the user-defined tolerances.

@@

%TODO: The following paragraph should probably be in a section about why late collisions are bad and why we want to avoid them.
To understand how late collisions lead to unstable collision response, we must first understand how in real-time collision detection works. In real-time physics engines, objects move in discrete steps. As a result of this, when two objects collide, they overlap each other i.e. penetrate. The collision is resolved by calculating the forces resulting from the collision and moving the objects so they no longer overlap (in PhysX if penetration is high, the latter may be done over several physics time-steps). If the penetration is high, such as in the case of a late collision response or if two objects are moving at high speed towards one another, the collision response can no longer guarantee stable results.

@@

Maximum penetration for a given speed occurs when two objects travelling directly towards each other have, in the final time-step before colliding the two objects have no distance between them, but are not overlapping, so not colliding. The next physics time-step, the collision will be detected and will have the maximum penetration possible for that relative speed. Re-arranging $s=d/t$, to $d=s.t$ and substituting the physics time-step for $t$, gives us the maximum distance (penetration) for a relative speed, and we are able to plot the maximum expected penetration line.

@@

In all the following experiments collisions were recorded, for each collision, the following data is contained: Relative Speed, the speed of the two colliding objects relative to each other; Penetration, the distance the two objects overlapped when the collision was detected. Note that PhysX reports penetration of collisions as negative values and can report collisions before the two objects are intersecting, which is recorded as a positive penetration. In all experiments, the penetration is negated for simplicity. The relative speed and penetration can be used to determine if the collision was a late collision. In all the following experiment scenarios only two objects are used, meaning if there was a missed collision there would be no collision output and multiple collisions from the same pair of objects can be ignored. The two objects start the scenario with a specified velocity (drag and gravity are disabled), the direction being directly towards the other object and the two objects were given the same speed and a random variation of between $0$ and $-1m\mathord{\cdot}s^{-1}$ to prevent identical results between iterations. Spheres were used, so rotational effects, such as rotational velocity, do not need to be accounted for. Thrashing between two objects on different servers is an unsolved problem in AP; thrashing occurrences can be detected by counting the number of migrations that occur before the first collision is detected, as only two objects are involved in each experiment, the number of migrations before a collision should only be one, otherwise thrashing has occurred. For the purposes of these experiments, collisions involving thrashing will be excluded, regardless of the correctness of the collision.

@@

Using the above method to detect late collisions, experiments on a distributed configuration of a simulation will now be performed. Experiments were carried out for both variations in all three aura tolerance factors and packet-loss. Experiments were conducted using AWS G2.2xlarge servers located within the same geographical region. A G2.2xlarge instance uses a 2.60GHz Intel Xeon E5-2670 CPU with 16GB RAM and an NVIDIA GRID K520 (Kepler) GPU running Ubuntu 18.04 LTS.

@@

Speed is controlled such that the two objects used in the experiment collide with each other with that desired speed. Latency is controlled using the Traffic Control tool to emulate latency for all communications between the servers. The desired latency is applied as a fixed delay to each server, resulting in that delay being applied to all packets outgoing from that server. Frame-time is controlled using a wait within the simulation's update loop, this is limited to a target frame-time as the resultant frame-times are a normal distribution with the target frame-time as the median. This is illustrated in Fig. \ref{fig_FrameTimeDensity}. As a result of this, half of all frames are expected to be above the target frame-time, which may cause false-positives in detecting late collisions, in the following experiments. However, the following points should be considered: the variance in frame-time is low; longer frames have to occur exactly at the time of messages being exchanged; exceeding one factor can be compensated for by having a low value in another factor. Therefore, false-positives are expected to be rare up until the tolerance value is approached. It should be noted that variance increases with target frame-time, therefore more false-positives should expected with experiments using higher target frame-times.

\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{FrameTimeDensity}
	\caption{Scaled Density of frame-times for the different target frame-times used in the collision correctness experiments. The median of each target frame-time is marked with a vertical dashed line.}
	\label{fig_FrameTimeDensity}
\end{figure}

@@

\subsubsection{Experiment parameters and output}
The two servers use the following tolerances unless otherwise stated: a maximum speed tolerance of $32m\mathord{\cdot}s^{-1}$; maximum latency tolerance of $2ms$; and a maximum frame-time tolerance of $15ms$. Each server has a random delay before starting between $0$ and the target frame-time in order to prevent the two servers always having synchronous update cycles. Each experiment is repeated $50$ times. An experiment was carried out for each aura tolerance value. The aura size for the varying tolerances are plotted and the tolerances used are marked. For each experiment, three tolerances values were chosen. For each tolerance value, the following output graphs were plotted:
\begin{itemize}
	\item The ratio of late to correct collisions and ratio of misses to total collision.
	\item The mean and $+/-2$ standard deviations of penetration time were plotted against each tolerance factor for each of the three tolerance values chosen.
\end{itemize}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{SpeedAuraSizes}
	\caption{Size of aura vs. speed tolerance. The speed tolerances used are marked in dashed lines}
	\label{fig_SpeedAuraSize}
\end{figure}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{RatiosVsSpeedLow}
	\caption{Ratio of Late to Correct Collisions and Misses to Total Collision vs. Speed using a speed tolerance of $16m\mathord{\cdot}s^{-1}$. The speed tolerance is marked in a dashed green line.}
	\label{fig_RatioVsSpeedLow}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{RatiosVsSpeedMid}
	\caption{Ratio of Late to Correct Collisions and Misses to Total Collision vs. Speed using a speed tolerance of $32m\mathord{\cdot}s^{-1}$. The speed tolerance is marked in a dashed green line.}
	\label{fig_RatioVsSpeedMid}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{RatiosVsSpeedHigh}
	\caption{Ratio of Late to Correct Collisions and Misses to Total Collision vs. Speed using a speed tolerance of $48m\mathord{\cdot}s^{-1}$. The speed tolerance is marked in a dashed green line.}
	\label{fig_RatioVsSpeedHigh}
\end{figure}

\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{MeanPenVsSpeedLow}
	\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying speed using a speed tolerance of $16m\mathord{\cdot}s^{-1}$. The maximum expected penetration time of 1 physics step is marked with a dashed blue line. The speed tolerance is marked in a dashed green line.}
	\label{fig_CollisionsPenVsSpeedLow}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{MeanPenVsSpeedMid}
	\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying speed using a speed tolerance of $32m\mathord{\cdot}s^{-1}$. The maximum expected penetration time of 1 physics step is marked with a dashed blue line. The speed tolerance is marked in a dashed green line.}
	\label{fig_CollisionsPenVsSpeedMid}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{MeanPenVsSpeedHigh}
	\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying speed using a speed tolerance of $48m\mathord{\cdot}s^{-1}$. The maximum expected penetration time of 1 physics step is marked with a dashed blue line. The speed tolerance is marked in a dashed green line.}
	\label{fig_CollisionsPenVsSpeedHigh}
\end{figure}
	%\label{fig_CollisionsPenVsSpeed}
%\begin{figure}
%	\centering
%	\includegraphics[width=\textwidth]{CollisionsPenVsSpeed}
%	\caption{Penetration time of objects with varying relative speed. Each red point represents one or more collisions. The maximum expected penetration time of 1 physics steps is marked with a dashed blue line. The speed tolerance is marked in a dashed green line. The number and magnitude of errors increases as relative speed increases beyond the tolerance.}
%	\label{fig_CollisionsPenVsSpeed}
%\end{figure}
%
%\begin{figure}
%\centering
%\includegraphics[width=\textwidth]{MeanMaxErrorVsSpeed}
%\caption{The mean and max of collision errors with varying relative speed}
%\label{fig_MeanMaxErrorVsSpeed}
%\end{figure}
%
%\begin{figure}
%\centering
%\includegraphics[width=\textwidth]{RatiosVsSpeed}
%\caption{The ratios of erroneous collisions to correct collisions and missed collisions to total collisions with varying relative speed}
%\label{fig_RatiosVsSpeed}
%\end{figure}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{LatencyAuraSizes}
	\caption{Size of aura vs. latency tolerance. The latency tolerances used are marked in dashed lines}
	\label{fig_LatencyAuraSize}
\end{figure}

Fig. \ref{fig_LatencyAuraSize} shows the size of the aura (not including the bounding sphere of the object) vs increasing latency tolerance, calculated using equation \ref{auraEquation}. The aura size increases discretely with latency tolerance, therefore we expect late collisions to begin one the aura size required for the latency is higher than what is needed for the tolerance. In the latency tolerance experiments, this will be when latency reaches $3ms$ for the $2ms$ tolerance experiments and $20ms$ for $15ms$ tolerance experiment. Note that late collisions are not expected for the $8ms$ experiment, as $20ms$ latency is not reached. False-positives are expected due to the frame-time delay method and should increase as latency increases.

\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{RatiosVsLatencyLow}
	\caption{Ratio of Late to Correct Collisions and Misses to Total Collision vs. Latency using a latency tolerance of $2ms$. The latency tolerance is marked in a dashed green line.}
	\label{fig_RatioVsLatencyLow}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{RatiosVsLatencyMid}
	\caption{Ratio of Late to Correct Collisions and Misses to Total Collision vs. Latency using a latency tolerance of $8ms$. The latency tolerance is marked in a dashed green line.}
	\label{fig_RatioVsLatencyMid}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{RatiosVsLatencyHigh}
	\caption{Ratio of Late to Correct Collisions and Misses to Total Collision vs. Latency using a latency tolerance of $16ms$. The latency tolerance is marked in a dashed green line.}
	\label{fig_RatioVsLatencyHigh}
\end{figure}

\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{MeanPenVsLatencyLow}
	\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying latency using a latency tolerance of $2ms$. The maximum expected penetration time of 1 physics step is marked with a dashed blue line. The latency tolerance is marked in a dashed green line.}
	\label{fig_CollisionsPenVsLatencyLow}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{MeanPenVsLatencyMid}
	\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying latency using a latency tolerance of $8ms$. The maximum expected penetration time of 1 physics step is marked with a dashed blue line. The latency tolerance is marked in a dashed green line.}
	\label{fig_CollisionsPenVsLatencyMid}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{MeanPenVsLatencyHigh}
	\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying latency using a latency tolerance of $16ms$. The maximum expected penetration time of 1 physics step is marked with a dashed blue line. The latency tolerance is marked in a dashed green line.}
	\label{fig_CollisionsPenVsLatencyHigh}
\end{figure}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{FrameAuraSizes}
	\caption{Size of aura vs. frame-time tolerance. The frame-time tolerances used are marked in dashed lines}
	\label{fig_FrameTimeAuraSize}
\end{figure}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{RatiosVsFrameTimeLow}
	\caption{Ratio of Late to Correct Collisions and Misses to Total Collision vs. frame-time using a frame-time tolerance of $8ms$. The frame-time tolerance is marked in a dashed green line.}
	\label{fig_RatioVsFrameTimeLow}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{RatiosVsFrameTimeMid}
	\caption{Ratio of Late to Correct Collisions and Misses to Total Collision vs. frame-time using a frame-time tolerance of $15ms$. The frame-time tolerance is marked in a dashed green line.}
	\label{fig_RatioVsFrameTimeMid}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{RatiosVsFrameTimeHigh}
	\caption{Ratio of Late to Correct Collisions and Misses to Total Collision vs. frame-time using a frame-time tolerance of $32ms$. The frame-time tolerance is marked in a dashed green line.}
	\label{fig_RatioVsFrameTimeHigh}
\end{figure}

\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{MeanPenVsFrameTimeLow}
	\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying frame-time using a frame-time tolerance of $8ms$. The maximum expected penetration time of 1 physics step is marked with a dashed blue line. The frame-time tolerance is marked in a dashed green line.}
	\label{fig_CollisionsPenVsFrameTimeLow}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{MeanPenVsFrameTimeMid}
	\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying frame-time using a frame-time tolerance of $15ms$. The maximum expected penetration time of 1 physics step is marked with a dashed blue line. The frame-time tolerance is marked in a dashed green line.}
	\label{fig_CollisionsPenVsFrameTimeMid}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{MeanPenVsFrameTimeHigh}
	\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying frame-time using a frame-time tolerance of $32ms$. The maximum expected penetration time of 1 physics step is marked with a dashed blue line. The frame-time tolerance is marked in a dashed green line.}
	\label{fig_CollisionsPenVsFrameTimeHigh}
\end{figure}

@@

\subsection{Thrashing}
In addition to recording the number of collisions that resulted in thrashing, the number of times an object thrashed between servers was also measured. The number of times thrashed is determined by measuring the number of migrations away from the server that the collisions takes place on, before the collision takes place. A histogram of the number of occurrences against the number of times thrashed is shown in Fig. \ref{fig_ThrashingHistogram}. For this histogram, data from the Frame-Time $33.33ms$ experiment is used, as this provides the largest sample of thrashing. As is demonstrated in Fig. \ref{fig_ThrashingHistogram}, the most frequent number of times thrashed is 1, by a large margin followed by a downward trend.

@@

@@

In addition to varying each aura tolerance factor, an experiment was carried out to determine the effects of packet-loss on the correctness of collisions between objects. In this experiment the packet-loss was varied from $0\%$ to $20\%$ in increments of $1\%$. The aura calculation does not account for packet-loss and and therefore there is no tolerance. Packet-loss is controlled using the Traffic Control tool; it is simulated on each server for all communication received from the other server.

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{RatiosVsLoss}
	\caption{The ratios of erroneous collisions to correct collisions and missed collisions to total collisions with varying packet loss.} %As packet-loss increases from $10\%$ to $20\%$ the ratio of erroneous collisions to correct collisions sharply increases as does misses to total collisions. Above $60\%$ packet-loss, all collisions are missed.}
	\label{fig_RatiosVsLoss}
\end{figure}

>>>>

\section{Scalability Experiments}
This study aims to measure and demonstrate scalability of AP. When more servers are added, the timeliness of the simulation improves and more objects may be supported. The performance measure of interest is the maximum frame time of a server as this indicates if the simulation can be maintained when object numbers increase (keeping a low frame-time is the goal). Therefore, an injection rate is used that spawns moving objects into the simulation as time passes.

@@

From these observations it can be concluded that this system is scalable in column configuration as the addition of servers results in increased performance.

@@

\section{Collision Correctness Experiments}
In the following section the correctness of collisions between objects is explored, i.e. do objects have the same collision behaviour in a AP as they do in a centralised system.

The following points highlight the contributions of the correctness experiments:
\begin{itemize}
	\item Demonstrate that collisions between objects and migrating are handled correctly as long as the factors (speed, frame-time, latency) remain within their tolerances. Collisions can be handled correctly under worsening conditions (higher speed, frame-time and latency), so long as the tolerances account for these.
	\item Demonstrate that late collisions begin to occur once tolerances are exceeded or as predicted by the aura calculation, i.e. auras are the size they need to be, and no larger, which would impact on performance.
	\item Demonstrate the severity of each of the factors being exceeded, i.e. when different factors are exceeded, how badly are collisions handled?
	\item Measure the frequency of two-object-thrashing
\end{itemize}

Experiments were undertaken to detect erroneous collisions under different conditions and are concerned with objects that are migrating and/or interacting with an object that has recently migrated. Erroneous collisions fall into two categories:
\begin{itemize}
	\item Missed collisions, collisions that should have taken place but were not detected by the physics engine e.g. Bullet through paper problem.
	\item Late collisions, collisions that were detected later than expected in a centralised simulation and result in not only different collision results, but also unstable collision response.
\end{itemize}

@@

It will now be explained how a naïve system can lead to erroneous collision behaviour and AP can lead to erroneous collision behaviour if speed, frame-time, or latency exceed the user-defined tolerances.

@@

%TODO: The following paragraph should probably be in a section about why late collisions are bad and why we want to avoid them.
To understand how late collisions lead to unstable collision response, it must first be understood how in real-time collision detection works, which is discussed in \ref{collision_detection}. In summary, in real-time physics engines, objects move in discrete steps. As a result of this, when two objects collide, they overlap each other i.e. penetrate. The collision is resolved by calculating the forces resulting from the collision and moving the objects so they no longer overlap (in PhysX if penetration is high, the latter may be done over several physics time-steps). If the penetration is high, such as in the case of a late collision response or if two objects are moving at high speed towards one another, the collision response can no longer guarantee stable results.

@@

Collision penetration can range from 0 to maximum penetration distance and depends upon the distance between the two objects' surfaces in the time-step before the collision. Maximum penetration for a given speed occurs when two objects are travelling directly towards each other and in the time-step before the collision occurs, there is no distance between the surfaces of the objects. In the next time-step, this results in the two objects overlapping each other with the maximum penetration for their relative speed. The overlap is then detected as a collision by the physics engine.  Re-arranging $s=d/t$, to $d=s.t$ and substituting the physics time-step for $t$, gives us the maximum distance (penetration) for a relative speed, and we are able to plot the maximum expected penetration line.

@@

In all the following experiments collisions were recorded, for each collision, the following data is contained: Relative Speed, the speed of the two colliding objects relative to each other; Penetration, the distance the two objects overlapped when the collision was detected. Note that PhysX reports penetration of collisions as negative values and can report collisions before the two objects are intersecting, which is recorded as a positive penetration. In all experiments, the penetration is negated for simplicity. The relative speed and penetration can be used to determine if the collision was a late collision. In all the following experiment scenarios only two objects are used, meaning if there was a missed collision there would be no collision output and multiple collisions from the same pair of objects can be ignored. The two objects start the scenario with a specified velocity (drag and gravity are disabled), the direction being directly towards the other object and the two objects were given the same speed and a random variation of between $0$ and $-1m\mathord{\cdot}s^{-1}$ to prevent identical results between iterations. Spheres were used, so rotational effects, such as rotational velocity, do not need to be accounted for.

Thrashing between two objects on different servers is an unsolved problem in AP; thrashing occurrences can be detected by counting the number of migrations that occur before the first collision is detected, as only two objects are involved in each experiment, the number of migrations before a collision should only be one, otherwise thrashing has occurred. For the purposes of these experiments, collisions involving thrashing will be excluded, regardless of the correctness of the collision.

@@

Using the above method to detect late collisions, experiments on a distributed configuration of a simulation were then performed. Experiments were carried out for both variations in all three aura tolerance factors and packet-loss. Experiments were conducted using AWS G2.2xlarge servers located within the same geographical region. A G2.2xlarge instance uses a 2.60GHz Intel Xeon E5-2670 CPU with 16GB RAM and an NVIDIA GRID K520 (Kepler) GPU running Ubuntu 18.04 LTS.

@@

Speed is controlled such that the two objects used in the experiment collide with each other with that desired speed. Latency is controlled using the Traffic Control tool to emulate latency for all communications between the servers. The desired latency is applied as a fixed delay to each server, resulting in that delay being applied to all packets outgoing from that server. Frame-time is controlled using a wait within the simulation's update loop, which is limited to a target frame-time as the resultant frame-times are a normal distribution with the target frame-time as the median. This is illustrated in Fig. \ref{fig_FrameTimeDensity}. As a result of this, half of all frames are expected to be above the target frame-time, which may cause false-positives in detecting late collisions, in the following experiments. However, the following points should be considered: the variance in frame-time is low; longer frames have to occur exactly at the time of messages being exchanged; exceeding one factor can be compensated for by having a low value in another factor. Therefore, false-positives are expected to be rare up until the tolerance value is approached. It should be noted that variance increases with target frame-time, therefore more false-positives should expected with experiments using higher target frame-times.

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{FrameTimeDensity}
	\caption{Scaled Density of frame-times for the different target frame-times used in the collision correctness experiments. The median of each target frame-time is marked with a vertical dashed line.}
	\label{fig_FrameTimeDensity}
\end{figure}

@@

\subsubsection{Experiment parameters and output}
The two servers use the following tolerances unless otherwise stated: a maximum speed tolerance of $32m\mathord{\cdot}s^{-1}$; maximum latency tolerance of $2ms$; and a maximum frame-time tolerance of $15ms$. Each server has a random delay before starting between $0$ and the target frame-time in order to prevent the two servers always having synchronous update cycles. Each experiment is repeated $50$ times. An experiment was conducted for each aura tolerance value. The aura size for the varying tolerances are plotted and the tolerances used are marked. For each experiment, three tolerances values were chosen. For each tolerance value, the following output graphs were plotted:
\begin{itemize}
	\item The ratio of late to correct collisions and ratio of misses to total collision.
	\item The mean and $+/-2$ standard deviations of penetration time were plotted against each tolerance factor for each of the three tolerance values chosen.
\end{itemize}

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{SpeedAuraSizes}
	\caption{Size of aura vs. speed tolerance. The speed tolerances used are marked in dashed lines}
	\label{fig_SpeedAuraSize}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{RatiosVsSpeedLow}
	\caption{Ratio of Late to Correct Collisions and Misses to Total Collision vs. Speed using a speed tolerance of $16m\mathord{\cdot}s^{-1}$. The speed tolerance is marked in a dashed green line.}
	\label{fig_RatioVsSpeedLow}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{RatiosVsSpeedMid}
	\caption{Ratio of Late to Correct Collisions and Misses to Total Collision vs. Speed using a speed tolerance of $32m\mathord{\cdot}s^{-1}$. The speed tolerance is marked in a dashed green line.}
	\label{fig_RatioVsSpeedMid}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{RatiosVsSpeedHigh}
	\caption{Ratio of Late to Correct Collisions and Misses to Total Collision vs. Speed using a speed tolerance of $48m\mathord{\cdot}s^{-1}$. The speed tolerance is marked in a dashed green line.}
	\label{fig_RatioVsSpeedHigh}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{MeanPenVsSpeedLow}
	\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying speed using a speed tolerance of $16m\mathord{\cdot}s^{-1}$. The maximum expected penetration time of 1 physics step is marked with a dashed blue line. The speed tolerance is marked in a dashed green line.}
	\label{fig_CollisionsPenVsSpeedLow}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{MeanPenVsSpeedMid}
	\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying speed using a speed tolerance of $32m\mathord{\cdot}s^{-1}$. The maximum expected penetration time of 1 physics step is marked with a dashed blue line. The speed tolerance is marked in a dashed green line.}
	\label{fig_CollisionsPenVsSpeedMid}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{MeanPenVsSpeedHigh}
	\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying speed using a speed tolerance of $48m\mathord{\cdot}s^{-1}$. The maximum expected penetration time of 1 physics step is marked with a dashed blue line. The speed tolerance is marked in a dashed green line.}
	\label{fig_CollisionsPenVsSpeedHigh}
\end{figure}
	%\label{fig_CollisionsPenVsSpeed}
%\begin{figure}
%	\centering
%	\includegraphics[width=\textwidth]{CollisionsPenVsSpeed}
%	\caption{Penetration time of objects with varying relative speed. Each red point represents one or more collisions. The maximum expected penetration time of 1 physics steps is marked with a dashed blue line. The speed tolerance is marked in a dashed green line. The number and magnitude of errors increases as relative speed increases beyond the tolerance.}
%	\label{fig_CollisionsPenVsSpeed}
%\end{figure}
%
%\begin{figure}
%\centering
%\includegraphics[width=\textwidth]{MeanMaxErrorVsSpeed}
%\caption{The mean and max of collision errors with varying relative speed}
%\label{fig_MeanMaxErrorVsSpeed}
%\end{figure}
%
%\begin{figure}
%\centering
%\includegraphics[width=\textwidth]{RatiosVsSpeed}
%\caption{The ratios of erroneous collisions to correct collisions and missed collisions to total collisions with varying relative speed}
%\label{fig_RatiosVsSpeed}
%\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{LatencyAuraSizes}
	\caption{Size of aura vs. latency tolerance. The latency tolerances used are marked in dashed lines}
	\label{fig_LatencyAuraSize}
\end{figure}

Fig. \ref{fig_LatencyAuraSize} shows the size of the aura (not including the bounding sphere of the object) vs increasing latency tolerance, calculated using equation \ref{auraEquation}. The aura size increases discretely with latency tolerance, for example tolerance values from $4ms$ to $20ms$ result in the same aura size. Late collisions are expected to occur only once the actual latency exceeds the maximum tolerance for the current aura size. In the following experiments, this means that in the $2ms$ tolerance experiments, late collisions are not expected to occur until the actual latency exceeds $3ms$. Likewise, in the $8ms$ and $16ms$ tolerance experiments, $20ms$ actual latency is expected to be reached before late collisions begin to occur. Note that late collisions are not expected for the $8ms$ experiment, as $20ms$ latency is not reached. False-positives are expected due to the frame-time delay method and should increase as actual latency increases.

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{RatiosVsLatencyLow}
	\caption{Ratio of Late to Correct Collisions and Misses to Total Collision vs. Latency using a latency tolerance of $2ms$. The latency tolerance is marked in a dashed green line.}
	\label{fig_RatioVsLatencyLow}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{RatiosVsLatencyMid}
	\caption{Ratio of Late to Correct Collisions and Misses to Total Collision vs. Latency using a latency tolerance of $8ms$. The latency tolerance is marked in a dashed green line.}
	\label{fig_RatioVsLatencyMid}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{RatiosVsLatencyHigh}
	\caption{Ratio of Late to Correct Collisions and Misses to Total Collision vs. Latency using a latency tolerance of $16ms$. The latency tolerance is marked in a dashed green line.}
	\label{fig_RatioVsLatencyHigh}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{MeanPenVsLatencyLow}
	\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying latency using a latency tolerance of $2ms$. The maximum expected penetration time of 1 physics step is marked with a dashed blue line. The latency tolerance is marked in a dashed green line.}
	\label{fig_CollisionsPenVsLatencyLow}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{MeanPenVsLatencyMid}
	\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying latency using a latency tolerance of $8ms$. The maximum expected penetration time of 1 physics step is marked with a dashed blue line. The latency tolerance is marked in a dashed green line.}
	\label{fig_CollisionsPenVsLatencyMid}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{MeanPenVsLatencyHigh}
	\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying latency using a latency tolerance of $16ms$. The maximum expected penetration time of 1 physics step is marked with a dashed blue line. The latency tolerance is marked in a dashed green line.}
	\label{fig_CollisionsPenVsLatencyHigh}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{FrameAuraSizes}
	\caption{Size of aura vs. frame-time tolerance. The frame-time tolerances used are marked in dashed lines}
	\label{fig_FrameTimeAuraSize}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{RatiosVsFrameTimeLow}
	\caption{Ratio of Late to Correct Collisions and Misses to Total Collision vs. frame-time using a frame-time tolerance of $8ms$. The frame-time tolerance is marked in a dashed green line.}
	\label{fig_RatioVsFrameTimeLow}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{RatiosVsFrameTimeMid}
	\caption{Ratio of Late to Correct Collisions and Misses to Total Collision vs. frame-time using a frame-time tolerance of $15ms$. The frame-time tolerance is marked in a dashed green line.}
	\label{fig_RatioVsFrameTimeMid}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{RatiosVsFrameTimeHigh}
	\caption{Ratio of Late to Correct Collisions and Misses to Total Collision vs. frame-time using a frame-time tolerance of $32ms$. The frame-time tolerance is marked in a dashed green line.}
	\label{fig_RatioVsFrameTimeHigh}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{MeanPenVsFrameTimeLow}
	\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying frame-time using a frame-time tolerance of $8ms$. The maximum expected penetration time of 1 physics step is marked with a dashed blue line. The frame-time tolerance is marked in a dashed green line.}
	\label{fig_CollisionsPenVsFrameTimeLow}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{MeanPenVsFrameTimeMid}
	\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying frame-time using a frame-time tolerance of $15ms$. The maximum expected penetration time of 1 physics step is marked with a dashed blue line. The frame-time tolerance is marked in a dashed green line.}
	\label{fig_CollisionsPenVsFrameTimeMid}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{MeanPenVsFrameTimeHigh}
	\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying frame-time using a frame-time tolerance of $32ms$. The maximum expected penetration time of 1 physics step is marked with a dashed blue line. The frame-time tolerance is marked in a dashed green line.}
	\label{fig_CollisionsPenVsFrameTimeHigh}
\end{figure}

@@

\subsection{Thrashing}
In addition to recording the number of collisions that resulted in thrashing, the number of times an object thrashed between servers was also measured. The number of times thrashed is determined by measuring the number of migrations away from the server that the collisions takes place on, before the collision takes place. A histogram of the number of occurrences against the number of times thrashed is shown in Fig. \ref{fig_ThrashingHistogram}. For this histogram, data from the Frame-Time $33.33ms$ experiment is used, as this provides the largest sample of thrashing. Fig. \ref{fig_ThrashingHistogram} demonstrates that the most frequent number of times thrashed is 1, by a large margin followed by a downward trend.

@@

The $2ms$ latency tolerance experiment exhibits more false-positives than the other experiments, including across the entire range of values used. This may be a result of small aura sizes producing more false-positive, the sample size being to small or another unknown effect which has not been accounted for. In addition, although late collisions increase as actual latency exceeds $20ms$ in the $15ms$ tolerance experiment, the mean $+2$ standard deviations does not exceed the maximum expected penetration line until $26ms$ actual latency is reached. Both of these unexpected results should be investigated further in the future.

@@

In addition to varying each aura tolerance factor, an experiment was undertaken to determine the effects of packet-loss on the correctness of collisions between objects. In this experiment the packet-loss was varied from $0\%$ to $20\%$ in increments of $1\%$. The aura calculation does not account for packet-loss and and therefore there is no tolerance. Packet-loss is controlled using the Traffic Control tool; it is simulated on each server for all communication received from the other server.

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{RatiosVsLoss}
	\caption{The ratios of erroneous collisions to correct collisions and missed collisions to total collisions with varying packet loss.} %As packet-loss increases from $10\%$ to $20\%$ the ratio of erroneous collisions to correct collisions sharply increases as does misses to total collisions. Above $60\%$ packet-loss, all collisions are missed.}
	\label{fig_RatiosVsLoss}
\end{figure}
